XToon

### 2013-04-07 paper/paper.tex

\documentclass[annual]{acmsiggraph}

\title{XToon}

@@

\section{Tone Detail}

\begin{equation}
 \sum_{j=1}^{z} j = \frac{z(z+1)}{2}
\end{equation}

\begin{eqnarray}
x & \ll & y_{1} + \cdots + y_{n} \\
  & \leq & z
\end{eqnarray}

>>>>

\documentclass[annual]{acmsiggraph}
\usepackage{wrapfig}
\title{XToon}

@@

\section{Tone Detail}
\begin{wrapfigure}{r}{0.1\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.1\textwidth]{images/xtoon_skin}
  \end{center}
  \caption{2D Texture.}
  \vspace{-10pt}
  \label{fig:2dtexture}
\end{wrapfigure}
We extend the concept of a regular toon shader by adding a second dimension to the texture. While the x-axis remains as $n\cdot l$, as in a classic toon shader, the y-axis represents the level of detail. The higher up on the axis, the less detail is used. Conversely, the lower the y-axis value, the more detail. An example of a 2D texture used in this application can be seen in Figure~\ref{fig:2dtexture}.

The method of computing the y-axis depends on an {\it{attribute map.}} The chosen attribute changes the level of detail, depending on its value. The original paper provided two possible attribute maps: distance and orientation. We implement distance, and probvide a new attribute map based on angle.

\subsection{Distance}
{\bf*{* Spencer to write in here**}}

We use the distance along the focal axis to determine. Also light directions are used somehow.

\subsection{Angle}
We introduce a new attribute map based on the angles of the {\it{look at}} of the camera and the surface normal. The look at vector is the direction that the camera is pointed. The angle between the two vectors is calculated using Equation~\ref{eqn:angle}, which is derived from the formula for dot product.

\begin{equation}
\label{eqn:angle}
a = \cos^{-1}{(-LookAt \cdot Normal / |LookAt||Normal|)}
\end{equation}
